{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}

### 2018-01-09 thesis/intro.tex
write intro organization section

@@

@@

\begin{itemize}
	\item {\bf Meaningful state spaces (Chapter \ref{chap:quicksand}).}
		I will present {\em Iterative Deepening}, a new algorithm for navigating the trade-off in how many preemption points to test at once.
		Iterative Deepening incorporates state space estimation \cite{estimation} to decide on-the-fly whether each state space is worth pursuing, and uses data race analysis \cite{tsan} to find new preemption point candidates based on a program's dynamic behaviour.
		This section will include a large evaluation of the technique, comparing its performance to three prior work approaches across 600+ unique tests.
		I will show that Iterative Deepening of preemption points outperforms prior work in terms both of finding bugs quickly and of completely verifying correctness when no bug exists.
	\item {\bf Educational use (Chapters \ref{chap:410} and \ref{chap:pintos}).}
		For the past five semesters, I have offered a fully-automated version of Landslide to students in 15-410, CMU's undergraduate Operating System Design and Implementation class \cite{kspec,thrlib}, for use as a debugging aid during the thread library project.
		Recently I have also extended Landslide to handle Pintos kernel projects from other universities \cite{pintos}.
		In the two most recent semesters, I collaborated with Operating Systems course staff at two such schools, the University of Chicago and University of California at Berkeley,
		to provide debugging feedback to their students.

		At all three universities I then collected statistics on the numbers and types of bugs found,
		and surveyed students to understand the human experience,
		This section will present the study's results
		to evaluate the suitability of stateless model checking in an educational setting.
	\item {\bf Transactional Memory (Chapter \ref{chap:tm}).}
		Transactional Memory (TM) is a relatively new concurrent programming technique \cite{transactional-memory}
		which is not yet addressed by modern model checkers.
		I have extended Landslide's concurrency model to support both hardware (HTM) and software (STM) variants of TM,
		and tested several ``real-world'' TM programs and benchmarks.
		This section will discuss the theoretical techniques I used to model the new form of concurrency,
		present associated correctness proofs of my approach,
		and show the testing results.
\end{itemize}

The rest of this dissertation is organized as follows.
% TODO(thesis):

>>>>

\subsection{Motivation}

@@

\subsection{Contribution}

@@

\begin{enumerate}
	\item {\bf Meaningful state spaces (Chapter \ref{chap:quicksand}).}
		I will present {\em Iterative Deepening}, a new algorithm for navigating the trade-off in how many preemption points to test at once.
		Iterative Deepening incorporates state space estimation \cite{estimation} to decide on-the-fly whether each state space is worth pursuing, and uses data race analysis \cite{tsan} to find new preemption point candidates based on a program's dynamic behaviour.
		This section will include a large evaluation of the technique, comparing its performance to three prior work approaches across 600+ unique tests.
		I will show that Iterative Deepening of preemption points outperforms prior work in terms both of finding bugs quickly and of completely verifying correctness when no bug exists.
	\item {\bf Educational use (Chapters \ref{chap:410} and \ref{chap:pintos}).}
		For the past five semesters, I have offered a fully-automated version of Landslide to students in 15-410, CMU's undergraduate Operating System Design and Implementation class \cite{kspec,thrlib}, for use as a debugging aid during the thread library project.
		Recently I have also extended Landslide to handle Pintos kernel projects from other universities \cite{pintos}.
		In the two most recent semesters, I collaborated with Operating Systems course staff at two such schools, the University of Chicago and University of California at Berkeley,
		to provide debugging feedback to their students.

		At all three universities I then collected statistics on the numbers and types of bugs found,
		and surveyed students to understand the human experience,
		This section will present the study's results
		to evaluate the suitability of stateless model checking in an educational setting.
	\item {\bf Transactional Memory (Chapter \ref{chap:tm}).}
		Transactional Memory (TM) is a relatively new concurrent programming technique \cite{transactional-memory}
		which is not yet addressed by modern model checkers.
		I have extended Landslide's concurrency model to support both hardware (HTM) and software (STM) variants of TM,
		and tested several ``real-world'' TM programs and benchmarks.
		This section will discuss the theoretical techniques I used to model the new form of concurrency,
		present associated correctness proofs of my approach,
		and show the testing results.
\end{enumerate}

\subsection{Organization}

The rest of this dissertation is organized as follows.

\begin{itemize}
	\item {\bf Background:} Chapter~\ref{chap:background} will present the requisite background material on concurrent programming, stateless model checking, and the various types of programs targeted by Landslide.

		{\bf Special personal note for the curious reader:} I have taken special care to write this chapter to be approachable by any intermediate programmer familiar with basic C programming concepts.
		My committee members obviously do not require such treatment, but I hope the rare reader who happens upon this work from outside my circle of research collaborators shall also not find the barrier to entry here too high.
		Concurrency analysis and verification is often very abstract,
		requiring strong intuition for certain concepts to understand the next algorithm that builds upon them, and so on;
		and I'd hate for any reader to get left behind off the bat for not knowing what a mutex is.
		%Abstract as the field is, it's also quite difficult to make good visual aids, unlike for example in graphics research, but I have done my best.
		Should you find any of my explanations insufficiently illuminating, no matter how far in the future you come from, please do get in touch.
	\item {\bf Landslide:} Chapter~\ref{chap:landslide} explains the design and implementation of Landslide,
		the core of my stateless model checking framework,
		and all the special features it's been equipped with over the years.
	\item {\bf Quicksand:} Chapter~\ref{chap:quicksand} presents the Iterative Deepening framework I've developed to more intelligently choose which state spaces to test, corresponding to contribution 1 above.
	\item {\bf Pebbles:} Chapter~\ref{chap:410} discusses my evaluation of Landslide in CMU's 15-410 class environment using the Pebbles kernel.
	\item {\bf Pintos:} Chapter~\ref{chap:410} discusses my evaluation of Landslide in the University of Chicago's and Berkeley's OS class environments using the Pintos kernel.
	\item {\bf Transactional Memory:} Chapter~\ref{chap:tm} presents my extension of Landslide's concurrency model to handle transactional concurrency and the evaluation thereof.
	\item {\bf Related Work:} Chapter~\ref{chap:relatedwork} honors my ancestors and neighbours in research spirit.
	\item {\bf Conclusion:} Chapter~\ref{chap:conclusion} hopes to leave you with thoughts on the future of this field.
\end{itemize}
